### 2017-07-13 architecture.tex
Adding meta-policy fig
Minor

To simplify and address concerns outlined in the previous section we introduce two
major changes. We introduce safe collections, an abstraction that encapsulates
a data-set and the set of policies that govern its use. Seconondly, in order to separate
administative responsibilities pertaining to the safe-collection from the infrastructure
admins, we create a new class of privileged users called Stewards. In this model, administrators
create a safe collection and hand over all administrative privileges to the stewards. This transfers
all administrative responsibilities regarding access and export of data to the stewards who now take
ownership and responsibility for the safe collection.

@@

Data-sets come with various levels of sensitivity and selecting the protocols to ensure adequate security
requires a case-by-case treatement. To closely integrate such policies with the data-set we have created
safe-collections. Safe collections allows the system administrators to partition the key administration
aspects of managing the relationship between analysts and a data to experienced curators of the data-set.
Safe-collections encapsulate a data-store where the dataset will reside, and a consistent set of policies
that controls access to data-store as well the policies themselves.

Since our existing production systems are built on Amazon Web Services(AWS), we have extended our work by
leverage services and guarantees provided by AWS. The data-store is implemented over S3 object store, and the
policies are implemented as Identity and Access Management(IAM) policies and S3 bucket policies.
A safe-collection is described in cloudformation, a JSON based software defined infrastructure system for AWS.
This allows our safe-collection descriptions to be reproducible and shareable.

Safe-collections enable the specification of limits and controls on access, usage and export of data.
The initial specification is a meta policy that defines the set of policies permissible on a safe-collection and
a steward group permitted to update the access policies. This meta policy schema translates to a form
at the creation of the safe-collection and is implemented as tags on the data-store. The schema is enforced
by the various services that interact with the safe-collection. The schema and the generated form are shown in
\figurename~\ref{fig:schema}

@@

% Public data
Public data-sets are assumed to contain no sensitive content and thus do not require access control nor
export control. Setting \texttt{SecurityClass} to \texttt{Public} indicates that the safe-collection does
not require a Steward and that all authenticated users on \NAME may access this dataset. None of the added
security features of safe-collections need apply.

@@

Here we will look at the two most common flows introduced by this model:

@@

Bob an analyst authenticates on the system and requests access to a private safe-collection.
The request is now visible on the stewarship dashboard of all stewards. Alice, a steward for the requested
safe-collection approves the request for n days. The approval process adds the appropriate policies to the
safe-collection granting access to Bob. Bob now can submit tasks via the  REST api, that specify data-items
from the safe-collection as inputs. The REST api marks the task as export controlled since it draws results
from an export controlled safe-collection. The submitted task is posted to an internal queue from which a
worker node in the \NAME private subnet picks up Bob's task. The worker node assumes Bob's identity and with
his credentials requests data from the safe-collection. Since Bob now has read privileges for the
safe-collection, the data is fetched to the worker node, on which the analysis task is executed.
Upon completion, the worker node puts the generated results under the outputs directory of the safe-collection
since the task used export controlled data. Bob's analysis is now complete, but he is unable to view the
results.

@@

Once Bob's analysis task is complete Bob realizes that he requires export approval before he may view the
results, so he issues a request for export. Alice, sees a new export request on her dashboard. Alice assumes
the steward role with a fresh authenticated token, and accesses the results and the complete description
of Bob's analysis task. Once Alice deems the results safe for export, she initiates data export. \NAME
services use Alice's temporary credentials to transfer the results from the safe-collection to a public
safe-collection and updates the task information with new location of the results. Bob can now log on
and view or download the results.

%\begin{figure}
%  \center
%  %\includegraphics[width=0.45\textwidth]{figures/arch.pdf}
%  \includegraphics[width=0.45\textwidth]{figures/safecollection.png}
%  \caption{Safe collection schema}
%  \label{fig:safe_schema}
%  \vspace{-1.5em}
%\end{figure}

>>>>

To address the concerns outlined in the previous section we introduce two
new abstractions: safe collections, an abstraction that encapsulates
a dataset and the set of policies that govern its use; and stewards, privileged users
to manage safe collections while separating administrative from infrastructure
administrators.  
In this model, administrators first define a safe collection and declare one 
or more stewards to manage that collection. This process transfers
all administrative responsibilities regarding access and export of data to the stewards.
%who now take ownership and responsibility for the safe collection.

@@

Datasets come with various levels of sensitivity. Selecting the policies, protocols, infrastructure, and 
software settings to ensure to ensure that individual datasets are adequately secured requires
case-by-case consideration. To represent these policies, such that dataset owners can manage these considerations
we define safe-collections. Safe-collections enable system administrators to partition the key administration
aspects of managing the relationship between analysts (data users/accessors) and data. 
Safe-collections encapsulate a data-store where the dataset will reside, and a consistent set of policies
that controls access to the data-store as well the policies themselves.

We extend our AWS-based Cloud Kotta services by leveraging additional
services and guarantees provided by AWS. 
Safe-collection policies are expressed on CLoud Kotta's S3-hosted data
%The data-store is implemented over S3 object store, and the
using Identity and Access Management(IAM) policies and S3 bucket policies.
A safe-collection is described in cloudformation, a JSON-based software defined infrastructure model for AWS.
This allows safe-collection descriptions to be verifiable, reproducible, and shareable.

Safe-collections offer a range of policies including specification of limits as well as management 
of access, usage, and data export. We define a meta-policy model via which administrators may define
the set of policies permissible on a safe-collection. Each safe-collection is associated with a steward
(or group of stewards) who may manage safe-collection policies. To simplify use, the meta policy schema 
is translated to a web-based form that can be completed by users during creation of a safe-collection. 
The completed form is stored as a set of special tags on the collection's data storage. The schema is enforced
by the various services that interact with the safe-collection. The schema and the generated form are shown in
\figurename~\ref{fig:schema}

@@

% Public data
Public datasets are assumed to contain no sensitive content and thus do not require access control nor
export control. Setting \texttt{SecurityClass} to \texttt{Public} indicates that the safe-collection does
not require a Steward and that all authenticated users on \NAME may access this dataset. None of the added
security features of safe-collections need apply.

@@

Here we describe the two most common flows introduced by this model:

@@

Bob an analyst authenticates on the system and requests access to a private safe-collection.
The request is now visible on the stewarship dashboard of all stewards. Alice, a steward for the requested
safe-collection approves the request for n days. The approval process adds the appropriate policies to the
safe-collection granting access to Bob. Bob now can submit tasks via the  REST api, that specify data-items
from the safe-collection as inputs. The REST api marks the task as export controlled since it draws results
from an export controlled safe-collection. The submitted task is posted to an internal queue from which a
worker node in the \NAME private subnet picks up Bob's task. The worker node assumes Bob's identity and with
his credentials requests data from the safe-collection. Since Bob now has read privileges for the
safe-collection, the data is fetched to the worker node, on which the analysis task is executed.
Upon completion, the worker node puts the generated results under the outputs directory of the safe-collection
since the task used export controlled data. Bob's analysis is now complete, but he is unable to view the
results. This flow is show in \figurename~\ref{fig:flow1}

@@

Once Bob's analysis task is complete Bob realizes that he requires export approval before he may view the
results, so he issues a request for export. Alice, sees a new export request on her dashboard. Alice assumes
the steward role with a fresh authenticated token, and accesses the results and the complete description
of Bob's analysis task. Once Alice deems the results safe for export, she initiates data export. \NAME
services use Alice's temporary credentials to transfer the results from the safe-collection to a public
safe-collection and updates the task information with new location of the results. Bob can now log on
and view or download the results. This flow is show in \figurename~\ref{fig:flow2}
